Simulating Ultra High-Dimensional Multivariate Data Using the bigsimr R Package

### 2020-06-20 030-bigsimr-package.Rmd
update case study with new syntax
draft rslurm section

```{r setup, eval = TRUE}
library(bigsimr)
# Reticulate needs to be able to find the python binary with `jax` installed
reticulate::use_condaenv("bigsimr-cpu")
```

## Basic use

short description

### Specifying marginals

@@

### Specify correlation

@@

### Small sample

@@

### Scaling up N

```{r, fig.width=7}
x <- rvec(100000, rho = rho, margins = margins, type = "spearman")

@@

### Evaluation

@@

>>>>

```{r setup, eval = TRUE}
## bookdown::preview_chapter('030-bigsimr-package.Rmd')
library(bigsimr)
```

## Specifying marginals

@@

## Specify correlation

@@

## Small sample

@@

## Scaling up N

```{r, fig.width=7}
x <- rvec(1e6, rho = rho, margins = margins, type = "spearman")

@@

## Evaluation

@@

## Easy cluster implementation through `rslurm`

Though `bigsimr` runs quickly, at large $d$ users may want to run jobs on a shared computing server. The R package `rslurm` makes it esay to run embarrasingly large parallel `rvec` calls. This example assumes that `bigsimr` is installed on a system
with a slurm scheduler installed.

```{r exampleRslurm, echo=FALSE, eval=FALSE, include=FALSE}
## run this code once and use the generated rds later.
## cyberhelp.sesync.org/rslurm/articles/rslurm.html
test_func <- function(par_mu, par_sd) {
    samp <- rnorm(10^6, par_mu, par_sd)
    c(s_mu = mean(samp), s_sd = sd(samp))
}
pars <- data.frame(par_mu = 1:10,
                   par_sd = seq(0.1, 1, length.out = 10))
library(rslurm)
sjob <- slurm_apply(test_func, pars, jobname = 'test_apply',
                    nodes = 2, cpus_per_node = 2, submit = TRUE)
list.files('_rslurm_test_apply', 'results')
res <- get_slurm_out(sjob, outtype = 'table')
head(res, 3)
cleanup_files(sjob) ## careful this deletes output also

## single function evaluation
sjob <- slurm_call(test_func, jobname = 'test_call',
                   list(par_mu = 5, par_sd = 1), submit = FALSE)

## try rvec
sjob <- slurm_call(rvec, jobname = 'rvec',
                   list(par_mu = 5, par_sd = 1), submit = FALSE)
```

```{r rvecRslurm, echo=TRUE, eval=FALSE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_single_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
sjob <- slurm_call(rvec, jobname = 'rvec',
                   list(n=1e6,
                        rho = rho,
                        margins = margins,
                        type = "spearman"),
                   submit = TRUE)

res <- readRDS(file.path('_rslurm_rvec', list.files('_rslurm_rvec', 'results')))
head(res, 3)
cleanup_files(sjob) ## careful this deletes output also
```

```{r rvecRslurmApply, echo=TRUE, eval=TRUE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_single_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
sjob <- slurm_call(rvec, jobname = 'rvec',
                   list(n=1e6,
                        rho = rho,
                        margins = margins,
                        type = "spearman"),
                   submit = TRUE)

res <- readRDS(file.path('_rslurm_rvec', list.files('_rslurm_rvec', 'results')))
head(res, 3)
cleanup_files(sjob) ## careful this deletes output also
```

### 2020-06-20 index.Rmd
draft rslurm section

```{r LoadLib, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
library(ggplot2)
library(tidyverse)
library(knitr)
library(dplyr)
## devtools::install_github( "adknudson/bigsimr", ref = 'develop')
set.seed(06082020)
```

>>>>

```{r LoadLib, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
library(ggplot2)
library(tidyverse)
library(knitr)
library(dplyr)
## rmote::start_rmote()
## library(ggplot2); qplot(mpg, wt, data=mtcars, colour=cyl)
## bookdown::serve_book()
set.seed(06082020)
```
